{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA

### 2021-11-24 paper/tex/sections/abstract.tex
update model E discussion

We present models for the properties of the population of Galactic double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA. We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with a new empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity. We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common-envelope, supernova and wind mass loss physics. We predict that, on average, for a 4(10)-year mission, LISA will detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs. The predicted BHBH rate remains notably consistent under most physics assumptions, whilst in contrast the BHNS rate varies widely across all of our assumptions, changing by up to 3 orders of magnitude, and the NSNS rate shows equally strong variations (albeit for a smaller subset of the physics assumptions). We show that altering the underlying physics assumptions can lead to contrasting population parameter distributions, even when detection rates are unchanged. We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population, as well as for disentangling the BHBH, BHNS and NSNS populations from each other. We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and the SKA.

>>>>

We present models for the properties of the population of Galactic double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA. We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with a new empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity. We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common-envelope, supernova and wind mass loss physics. We predict that, on average, for a 4(10)-year mission, LISA will detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs. The predicted BHBH rate remains notably consistent under most physics assumptions, whilst in contrast the BHNS rate varies widely across all of our assumptions, changing by up to 3 orders of magnitude, and the NSNS rate shows equally strong variations (albeit for a smaller subset of the physics assumptions). We show that altering the underlying physics assumptions can lead to contrasting population parameter distributions, even when detection rates are unchanged. We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population, as well as for disentangling the BHBH, BHNS and NSNS populations from each other. We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and the Square Kilometre Array (SKA).

### 2021-11-24 paper/tex/sections/discussion.tex
update model E discussion

In this section we discuss the prospects of (and methods for) identifying LISA sources (Sec.~\ref{sec:identify_sources}), the possibility of matching LISA signals to SKA detections (Sec.~\ref{sec:pulsar_matching}) and the main caveats for this study (Sec.~\ref{sec:caveats}). All statistics quoted in each subsection are for the fiducial (model \modFid{}) model. However, we find that the \textit{fraction} of systems for each statistic are robust over different model variations (though the total numbers for each statistic change over our model variations due to the different detection rates).

@@

\subsubsection{Distinguishing from WDWD population}\label{sec:WDWD_distinguish}
The simplest way to check whether a source is a WDWD is to evaluate its chirp mass. The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.2 \unit{M_{\odot}}$. Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + \Delta \mathcal{M}_c$ must not be a WDWD (where $\Delta \mathcal{M}_c$ is calculated using Eq.~\ref{eq:chirp_mass_uncertainty}). We find that for the detectable population of a 4(10)-year LISA mission, \BHBHAboveMaxWDWDFourPerc{}(\BHBHAboveMaxWDWDTenPerc{})\% of BHBHs, \BHNSAboveMaxWDWDFourPerc{}(\BHNSAboveMaxWDWDTenPerc{})\% of BHNSs and \NSNSAboveMaxWDWDFourPerc{}(\NSNSAboveMaxWDWDTenPerc{})\% of NSNSs satisfy this condition. This method is not particularly effective for NSNSs since their average chirp mass, $1.17 \unit{M_\odot}$, is below the Chandrasekhar limit.

Another discriminator between WDWDs and other DCOs is eccentricity. WDWDs formed in the disc are thought to be formed mainly through isolated binary formation and have little to no eccentricity (e.g.\ \citealt{Nelemans+2001}, see however \citealt{Dosopoulou+2016a, Dosopoulou+2016b, Gosnell+2019}). This is because WDWDs formed through isolated binary evolution all experience a phase of mass transfer or a common envelope, which typically circularises the binary \citep[e.g.][]{Marsh+2004}. However, in contrast to the more massive DCOs that we study, WDWDs do not experience strong natal kicks which we find to be the main source of eccentricity. Therefore, if any system is detected with anything other than one detectable harmonic, this suggests that the system is unlikely to be a WDWD. We find that for a 4(10)-year LISA mission, \BHBHMultipleHarmonicsFourPerc{}(\BHBHMultipleHarmonicsTenPerc{})\% of BHBHs, \BHNSMultipleHarmonicsFourPerc{}(\BHNSMultipleHarmonicsTenPerc{})\% of BHNSs and \NSNSMultipleHarmonicsFourPerc(\NSNSMultipleHarmonicsTenPerc{})\% of NSNSs are detected with multiple harmonics. Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.~\ref{sec:fiducial_distributions}).

However, we should also consider that eccentric WDWDs could be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}, or with third companions \citep[e.g.][]{Antonini+2017}. This means that we cannot assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane (though even then there is a chance they were formed dynamically). We can use the sky localisation, scale height of the disc and distance to the source to estimate what fraction of eccentric sources can be localised to the Galactic plane. This condition can be written as $\sigma_\theta < \arcsin(z_{\rm plane} / D_L)$ or $D_L < z_{\rm plane}$, where we set the height of the Galactic plane, $z_{\rm plane}=0.95 \unit{kpc}$, to the scale height of the high-$\alpha$ disc. We apply this condition to find that the fraction of sources that are eccentric \textit{and} localised within the disc for a 4(10)-year LISA mission are \BHBHEccInDiscFourPerc{}(\BHBHEccInDiscTenPerc{})\% for BHBHs, \BHNSEccInDiscFourPerc{}(\BHNSEccInDiscTenPerc{})\% for BHNSs and \NSNSEccInDiscFourPerc{}(\NSNSEccInDiscTenPerc{})\% for NSNSs. Note that although the fractions are the same for the 10-year mission, the \textit{absolute} number of detections is still greater. Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population. Thus we will be able to confidently discuss approximately half of all detected sources from WDWDs. This increases to roughly 60\% for a 10-year mission.

We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of \textit{distinguishable} detections increases by a greater factor since each of the more numerous sources are better measured. This further underlines the benefits of extending the LISA mission to 10 years.

@@

\subsection{Matching LISA detections to pulsars with SKA}\label{sec:pulsar_matching}
Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main type of electromagnetic counterpart for this population is pulsars. Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar. The joint detection of a binary pulsar with LISA and SKA would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics. A pulsar(PSR)+BH can provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}. Alternatively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magnitude more accurately than other proposed observational constraints \citep{Kyutoku+2019, Thrane+2020}.

We estimate that on average, given the number of detectable pulsars and SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}). Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in SKA. By considering Fig.~\ref{fig:ang_res}, approximately $11$ and $6$ (for SKA-1 and SKA-2) DCOs will satisfy this constraint.

@@

Our predictions are subject to various uncertainties which can be broadly divided into different categories: (a) those arising from the progenitor models for the population of DCOs and (b) those arising from the choices we have made when placing these DCOs in our model for the Milky-Way. Furthermore, (c) there may be contributions from other formation channels that we have not considered here. Although we are unable, at present, to evaluate the impact of all these uncertainties, the reader should nevertheless keep in mind that they are likely very substantial. Most of these concerns are not unique to these study, but apply to most of the predictions available in present literature. We highlight a few main concerns.

@@

\paragraph{Other formation channels (c)} In this work we considered the formation of double compact objects through the isolated binary formation channel. We have not included the possible contributions from other channels such as dynamical formation in dense star clusters, formation in young star clusters and triple systems in the field. We refer to \citet{Kremer+2018} and \citet{Banerjee+2020} for a studies of the contribution of dynamical formation in globular and young stellar clusters.

>>>>

In this section we discuss the prospects of (and methods for) identifying LISA sources (Sec.~\ref{sec:identify_sources}), the possibility of matching LISA signals to SKA detections (Sec.~\ref{sec:pulsar_matching}) and the main caveats for this study (Sec.~\ref{sec:caveats}). All predictions quoted in each subsection are derived for the fiducial (model \modFid{}) model.

@@

\subsubsection{Distinguishing from WDWD population}\label{sec:WDWD_distinguish}
The simplest way to check whether a source is a WDWD is to evaluate its chirp mass. The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.2 \unit{M_{\odot}}$. Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + \Delta \mathcal{M}_c$ must not be a WDWD (where $\Delta \mathcal{M}_c$ is the error on the chirp mass, estimated using Eq.~\ref{eq:chirp_mass_uncertainty}). We find that for the detectable population of a 4(10)-year LISA mission, \BHBHAboveMaxWDWDFourPerc{}(\BHBHAboveMaxWDWDTenPerc{})\% of BHBHs, \BHNSAboveMaxWDWDFourPerc{}(\BHNSAboveMaxWDWDTenPerc{})\% of BHNSs and \NSNSAboveMaxWDWDFourPerc{}(\NSNSAboveMaxWDWDTenPerc{})\% of NSNSs satisfy this condition. This method is not particularly effective for NSNSs since their average chirp mass, $1.17 \unit{M_\odot}$, is below the Chandrasekhar limit.

Another discriminator between WDWDs and other DCOs is eccentricity. WDWDs formed in the disc are thought to be formed mainly through isolated binary formation and have little to no eccentricity (e.g.\ \citealt{Nelemans+2001}, see however \citealt{Dosopoulou+2016a, Dosopoulou+2016b, Gosnell+2019}). This is because WDWDs formed through isolated binary evolution all experience a phase of mass transfer or a common envelope, which typically circularises the binary \citep[e.g.][]{Marsh+2004}. However, in contrast to the more massive DCOs that we study, WDWDs do not experience strong natal kicks which we find to be the main source of eccentricity. Therefore, if any system is detected with anything other than one detectable harmonic, this suggests that the system is unlikely to be a WDWD. We find that for a 4(10)-year LISA mission, \BHBHMultipleHarmonicsFourPerc{}(\BHBHMultipleHarmonicsTenPerc{})\% of BHBHs, \BHNSMultipleHarmonicsFourPerc{}(\BHNSMultipleHarmonicsTenPerc{})\% of BHNSs and \NSNSMultipleHarmonicsFourPerc(\NSNSMultipleHarmonicsTenPerc{})\% of NSNSs are detected with multiple harmonics (see also Sec.~\ref{sec:fiducial_distributions}). Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.~\ref{sec:fiducial_distributions}).

However, we should also consider that eccentric WDWDs could be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}, or with third companions \citep[e.g.][]{Antonini+2017}. This means that we cannot assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane (though even then there is a chance they were formed dynamically). We can use the sky localisation, scale height of the disc and distance to the source to estimate what fraction of eccentric sources can be localised to the Galactic plane. This condition can be written as $\sigma_\theta < \arcsin(z_{\rm plane} / D_L)$ or $D_L < z_{\rm plane}$, where we set the height of the Galactic plane, $z_{\rm plane}=0.95 \unit{kpc}$, to the scale height of the high-$\alpha$ disc. We apply this condition to find that the fraction of sources that are eccentric and localised within the disc for a 4(10)-year LISA mission are \BHBHEccInDiscFourPerc{}(\BHBHEccInDiscTenPerc{})\% for BHBHs, \BHNSEccInDiscFourPerc{}(\BHNSEccInDiscTenPerc{})\% for BHNSs and \NSNSEccInDiscFourPerc{}(\NSNSEccInDiscTenPerc{})\% for NSNSs. Note that although the fractions are the same for the 10-year mission, the absolute number of detections is still greater. Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population. Thus we will be able to confidently discuss approximately half of all detected sources from WDWDs. This increases to roughly 60\% for a 10-year mission.

We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of distinguishable detections increases by a greater factor since each of the more numerous sources are better measured. This further underlines the benefits of extending the LISA mission to 10 years.

@@

\subsection{Matching LISA detections to pulsars with the SKA}\label{sec:pulsar_matching}
Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main type of electromagnetic counterpart for this population is pulsars. Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar. The joint detection of a binary pulsar with LISA and the SKA \citep{Dewdney+2009} would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics. A pulsar(PSR)+BH can provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}. Alternatively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magnitude more accurately than other proposed observational constraints \citep{Kyutoku+2019, Thrane+2020}.

We estimate that on average, given the number of detectable pulsars and the SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}). Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in SKA. By considering Fig.~\ref{fig:ang_res}, approximately $11$ and $6$ (for SKA-1 and SKA-2) DCOs will satisfy this constraint.

@@

Our predictions are subject to various uncertainties which can be broadly divided into different categories: (a) those arising from the progenitor models for the population of DCOs and (b) those arising from the choices we have made when placing these DCOs in our model for the Milky-Way. Although we are unable, at present, to evaluate the impact of all these uncertainties, the reader should nevertheless keep in mind that they are likely very substantial. Most of these concerns are not unique to these study, but apply to most of the predictions available in present literature. We highlight a few main concerns.

@@

\subsection{Other formation channels}

In this paper we considered the formation of NS and BH binaries formed through isolated binary evolution through the classical CE channel, the stable mass transfer channel and variations on these (e.g. Fig.~\ref{fig:formation_channels}).  We did not consider further possible contributions from other formation channels, which may play a role.

We highlight the possible role of dynamical formation in globular clusters \citet[e.g.\ ][]{Kremer+2018}. For a nominal 4-year LISA mission, they estimate 21 sources in total of which 7 are binary black holes.

\citet{Banerjee+2020} investigates formation in young star clusters and estimates xxx sources

several 10s to 100s systems with SNR>5

### 2021-11-24 paper/tex/sections/introduction.tex
update model E discussion

One particularly interesting class of potential LISA sources is BHNSs. With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}. However, with only two detections (not including the low-confidence candidate GW190426 \citealt{Abbott+2020_GWTC2} or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1} ) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain. Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Mandel+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars. Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts. A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}. These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and SKA, which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.

>>>>

One particularly interesting class of potential LISA sources is BHNSs. With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}. However, with only two detections (not including the low-confidence candidate GW190426 \citealt{Abbott+2020_GWTC2} or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1} ) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain. Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Mandel+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars. Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts. A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}. These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and the Square Kilometre Array (SKA, \citealt{Dewdney+2009}), which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.

### 2021-11-24 paper/tex/sections/results.tex
update model E discussion

When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBHs and then BHNSs. To understand this it is helpful to consider how the inspiral time scales with various parameters \citep{Peters+1964}
\begin{equation}
    t_{\rm inspiral} \propto \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
\end{equation}
The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}). The detectable NSNS systems have the tightest orbits at DCO formation. The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for detectable BHBH:BHNS:NSNS in our simulations. This results in increase of the inspiral time by a factor of about 4000:80:1. The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured. The median total masses differ by ratios of 6:4:1 for detectable BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations. The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and so is not of interest. The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$. The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\%, and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:dco_formation_properties}.

>>>>

When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBHs and then BHNSs. To understand this it is helpful to consider how the inspiral time scales with various parameters \citep{Peters+1964}
\begin{equation}
    t_{\rm inspiral} \propto \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
\end{equation}
The inspiral time depends most strongly on the separation at DCO formation, $a$, and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}). The detectable NSNS systems have the tightest orbits at DCO formation. The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for detectable BHBH:BHNS:NSNS in our simulations. This results in increase of the inspiral time by a factor of about 4000:80:1. The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured. The median total masses differ by ratios of 6:4:1 for detectable BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations. The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and so is not of interest. The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$. The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\%, and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:dco_formation_properties}.

### 2021-11-24 paper/tex/sections/variations.tex
update model E discussion

In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE. This effectively excludes any systems that evolve through case BB mass transfer since all common-envelopes initiated in this way have donors in the Hertzsprung gap and thus end as stellar mergers under the pessimistic CE assumption. Therefore, this kills nearly all NSNS systems. We also find a heavy reduction of the BHNS systems by a factor 6. The BHBH systems are not affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.

Finally, in model \modCaseBBOpt{}, we again enforce that case BB mass transfer is always unstable, but in combination with the optimistic treatment for CE (essentially combining models \modCaseBB{} and \modOpt{}). This allows the systems formed through case BB (as well as any other systems that have HG donors for common-envelopes) to survive the CE phase. We find that this model leads to the highest predictions for the detections among all variations that we have considered.

>>>>

In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE. Note that this is slightly different from model E from \citet{Broekgaarden+2019}, as we allow Helium Hertzsprung Gap donors to survive a common-envelope (but still apply the pessimistic CE assumption in all other cases). We make this change since, otherwise, the model would effectively exclude any systems that evolve through case BB mass transfer and kill nearly all NSNS systems. Therefore, in model \modCaseBB{}, we find that case BB systems form through a common-envelope phase rather than only stable mass transfer (see Fig.~\ref{fig:formation_channels}). This model gives the lowest NSNS rate of all of our variations, which is a factor of 3 lower than our fiducial rate.  We also find a reduction of the BHNS systems by a factor 2. The BHBH systems are not significantly affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.

Finally, in model \modCaseBBOpt{}, we again enforce that case BB mass transfer is always unstable, but in combination with the optimistic treatment for CE (essentially combining models \modCaseBB{} and \modOpt{}). This allows the systems  that have HG donors for common-envelopes (as well as those formed through case BB mass transfer) to survive the CE phase. We find that this model leads to the highest predictions for the detections among all variations that we have considered.
